Aggressive Scheduling for Numerical Programs

### 2012-05-02 report/draft.tex
Fix some typos. Add more references.

\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsfonts}   % if you want the fonts
\usepackage{amssymb}    % if you want extra symbols
\usepackage{listings}
%\usepackage{savetrees}

@@

With software pipelining, we can reduce
pipeline stalls in the hardware, since the pipeline can be fed with new instructions from
different loop iterations. This greatly increases instruction parallelism because we can
start a new loop iteration before the past ones have completed. For this technique to be
effective, each loop is transformed into three sections:

@@

\subsection{Enforcing a Schedule}
\begin{verbatim}
+(X) How do we enforce a schedule at the C level?
+( ) What does the code look like?
+(X) Would this hack always work? Either way it would be ideal to have a flag
     or pragma to allow the user to choose a schedule.

\end{verbatim}
Most modern compilers do not preserve instruction ordering imposed at the.
input language level, and instead rely on general purpose methods such
as \emph{list scheduling} to order instructions. In the common case this frees
the developer from the task of determining an efficient schedule, but in our
case this feature serves as a roadblock. While the GCC~\cite{} provides flags for
disabling instruction scheduling it comes at the cost of overall
performance because we only plan to schedule loop code. Moreover, our plan
involves using the Intel Compiler~\cite{}, thus we need a general solution for
scheduling at the C code level.

@@

For our purposes this technique proved itself effective for enforcing a
schedule, but in some cases the GCC would add superfluous instructions. Thus
in the future a more general approach, such as a compiler directive, would be
advantageous.

@@

>>>>

\usepackage{url}
\usepackage{verbatim}
\usepackage{amsmath}
\usepackage{amsfonts}   % if you want the fonts
\usepackage{amssymb}    % if you want extra symbols
\usepackage{listings}
%\usepackage{savetrees}

@@

With software pipelining, we can reduce
pipeline stalls in the hardware, since the pipeline can be fed with new instructions from
different loop iterations. This greatly increases instruction parallelism because we can
start a new loop iteration before the past ones have completed. For this technique to be
effective, the loop is transformed into three sections:

@@

\subsection{Enforcing a Schedule}
\begin{comment}
+(X) How do we enforce a schedule at the C level?
+( ) What does the code look like?
+(X) Would this hack always work? Either way it would be ideal to have a flag
     or pragma to allow the user to choose a schedule.

\end{comment}

Most modern compilers do not preserve instruction ordering imposed at the
input language level, and instead rely on general purpose methods such
as \emph{list scheduling} to order instructions. In the common case, this frees
the developer from the task of determining an efficient schedule, but in our
case this feature serves as a roadblock. While the GCC~\cite{gccwebsite} provides flags for
disabling instruction scheduling it comes at the cost of overall
performance because we only plan to schedule loop code. Moreover, our plan
involves using the Intel Compiler~\cite{iccwebsite}, thus we need a general solution for
scheduling at the C code level.

@@

For our purposes this technique proved itself effective for enforcing a
schedule, but in some cases the GCC compiler would add superfluous instructions. Thus
in the future a more general approach, such as a compiler directive, would be
advantageous.

@@

\section{Post-mortem and Final Notes}

We propose distributing the credit as XX\% to Richard, XX\% to Flávio and XX\% to Berkin.
XXX Richard did this, Flavio did that, Berkin did ...
